A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
OKay
corrections

\begin{figure}[h]
  \centering
  \input{figures/dora}
  \caption{A exploration domain with three rooms and 13 places. The
    robot is in in the centre of room A}
\label{fig:dora2}
\end{figure}
An instance of this domain is shown in figure \ref{fig:dora2}. Basic
types of element are{\tt rooms}, {\tt places} and {\tt
  objects}. Places are topological map nodes that occur in rooms.
Objects, including the robot, are always located at a place. The robot
can move around the rooms via connections between places given by the
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

The robot can find out if an object is at a certain place by executing
the {\tt look-for-object} action. Moreover, the contents of a room
indicates its category, and certain objects are more likely to be
located in rooms of certain categories. For example, a box of
cornflakes is more likely to be located in the kitchen than the
office. The {\tt look-for-object} might result in a positive
perception if the object is there. An instantaneous positive detection
of the object is not proof positive that it is there. Also, some
objects are harder to detect than others. Also, Additionally, if the
robot is in the presence of a human, it can ask what type of room they
are currently in, however conducting a dialogue is more costly than
running a vision algorithm (cost of 8 vs costs of 3).

We perform experiments on tasks of several sizes. The robot's
objective is to find one or more objects and report back their
position to a person. In order to determine the impact of sensor
reliability in a comparison with the baseline, we also run tests on
identical problems but changed the sensor model for the target
objects: the probability for perceiving the object if it was there
went from 0.9 in the easiest case to 0.65 and 0.4 in the average and
hard cases respectively. In addition, we test how our system performs
in tasks requiring indirect sensing. Here, we gave the planner rewards
for visiting a certain type of room (e.g. kitchen or office). We did
not place any humans in those scenarios, so the only way of
determining the room category is by looking for objects typical for
that room type. As this indirect reasoning is a tasks that cannot be
performed by the continual planner alone, we did not run the baseline
system on those problems.

In our evaluation we run 50 simulations in each configuration. The
planning and simulation models are in exact correspondence. Not all
problems have a solution, so we also examine whether or not detection
of the non-existence of a solution is important in stochastic domains.
%% 
We perform multiple tests with different limits for the
belief-space size in contingent sessions.  Higher limits result in
longer contingent planning times and higher plan quality.

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs}
  \label{fig:results-quality}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \input{figures/dora}
  \caption{A exploration domain with three rooms and 13 places. The
    robot is in in the centre of room A}
\label{fig:dora2}
\end{figure}
An instance of this domain is shown in figure \ref{fig:dora2}. Basic
types of element are {\tt rooms}, {\tt places} and {\tt
  objects}. Places are topological map nodes that occur in rooms.
Objects, including the robot, are always located at a place. The robot
can move around the rooms via connections between places given by the
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

The robot can look for an object at a place by executing a {\tt
  look-for-object} action. Moreover, the contents of a room indicate
its category, because certain objects are more likely to be located in
rooms of particular categories. For example, a box of cornflakes is
more likely to be located in the kitchen than the office. Executing
{\tt look-for-object} results in a noisy sensing outcome, sometimes
indicating a positive perception if the object is there. Here, some
objects are harder to detect than others. Lastly, if the robot is in
the presence of a human, it can ask what type of room it is currently
in, however conducting a dialogue is more costly than running a vision
algorithm (cost of 8 vs costs of 3).

%%  Therefore, an instantaneous positive detection of an object is
%% not proof positive of it being there.

We perform experiments on tasks of several sizes. The objective is to
find one or more objects and report their position to the user. In
order to determine the impact of the reliability of sensing in a
comparison with the baseline, we run tests on identical problems but
changed the sensor model for the target objects: the probability for
perceiving the object if it was there went from 0.9 in the easiest
case to 0.65 and 0.4 in the average and hard cases respectively. In
addition, we test how our system performs in tasks requiring indirect
sensing. Here, we gave the planner rewards for visiting a certain type
of room (e.g. kitchen or office). We did not place any humans in those
scenarios, so the only way of determining the room category is by
looking for objects typical for that room type. As this indirect
reasoning is a tasks that cannot be performed by the continual planner
alone, we did not run the baseline system on those problems.

In our evaluation we run 50 simulations in each configuration. A run
timeouts after 30 minutes (1800 seconds). The planning and simulation
models are in exact correspondence. Not all problems have a solution,
so we also examine whether or not detection of the non-existence of a
solution is important in stochastic domains.
%% 
We perform multiple tests with different limits for the
belief-space size in contingent sessions.  Higher limits result in
longer contingent planning times and higher plan quality.

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

### 2010-11-29 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
corrections

We describe our continual planning approach that switches between
sequential and contingent sessions. This proceeds by interleaved
planning and execution in a deterministic-action POMDP described in
DTPDDL. During a sequential session, planning is performed by a
``classical'' system,\footnote{That is, a system designed to solve
fully observable deterministic tasks.}  and execution proceeds
according to the {\em trace} computed by that system. Taking the form
of a classical plan, the trace specifies a sequence of POMDP
actions that achieve the agent's objectives in a deterministic
approximation, i.e., {\em determinisation}, of the problem at
hand. More precisely, the trace is an interleaved sequence of POMDP
actions and {\em assumptive} actions. The latter correspond to
assumptions the planner makes about the truth value of {\em runtime
state variables} -- e.g. that a box of cornflakes is located in the
kitchen at the third plan step. Another kind of assumption, called an
{\em applicability} assumption, is made when the trace includes an
action $\action$ that is not applicable with probability $1$ at the
belief-state
\bstate\ that the system is projected to be in when \action\ is
scheduled for execution, i.e., $\exists\state\in\states\;
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

Our approach always begins with a sequential session. Non-assumptive
actions from the trace are executed until the applicability of the
next scheduled action is uncertain.  A contingent session then begins,
which tailors sensory processing by the agent to determine whether the
assumptions made in the trace hold. For each {\em active} assumption
in the trace, we add a {\em disconfirm} action to the POMDP whose
execution is rewarding (resp. costly) if the assumption is false
(resp. true). We also add one {\em confirm} action that is rewarding
(resp. costly) to execute if $\poss(\action)$ is true
(resp. false). If execution of the contingent plan applies a
disconfirm action, then a new sequential session begins at the current
underlying belief-state. If the confirm action is executed, the
sequential session is resumed, and
\switchAction\ is executed. Otherwise, control rests in the continual
session.

Because contingent planning is only practical in relatively small
POMDPs, contingent sessions proceed in an abstract decision process
determined by the current trace. That abstract process is constructed
by first omitting all variables from the model that are not featured
in the trace, and by then iteratively refining that abstraction while
the resulting model is of a practicable size.

Finally, whether proceeding in a sequential or contingent session, our
continual planner maintains a factored representation of successive
{\em belief-states}, by performing belief revision according to
Eq~\ref{eq:revision}. Moreover, our internal representation of that
distribution corresponds more-or-less directly to an $(\pp{:init})$
declaration in DTPDDL. Our approach uses that {\em underlying}
belief-state as: (1) the source of determinisations for sequential
planning, (2) the basis for switching, and (3) the source for state
abstraction in contingent sessions.

@@

A sequential session uses a classical planner to compute a trace. The
latter encapsulates assumptions about: (1) the true underlying state,
(2) how the plan's execution will progress, and (3) the possibility of
the agent eventually holding strong beliefs about the truth values of
specific state propositions. Here we describe the deterministic
planning problem, derived from the DTPDDL model, that admits plans
which correspond to traces.

In a deterministic-action POMDP all the uncertainty in state and
action is expressed in the $(\pp{:init})$ DTPDDL declaration. Our
approach uses the structure of that, as it occurs in the problem
description, to define a set of state-assumptions available to
sequential planning.
%%
Writing \#\ if the value of a proposition is unspecified, for
$\pp{DORA}$ we have the following assumptions:

@@

\noindent In detail, a valid assumption in our setting corresponds to a {\em
relaxed} visitation of the root term of $(\pp{:init})$. In this
relaxed case, a conjunctive term is visited iff its atomic subterms
are visited, and zero or more of its immediate probabilistic subterms
are visited. The starting state, $\state_0$, for sequential planning
is an {\em abstract} state that captures the unique assumption which
has probability $1.0$. In $\pp{DORA}$, that is:

@@

In order to make assumptions available to the sequential planner, we
add one {\em assumptive} action $\assumptiveS{i}$ to the problem for
each element, $p_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. The physics of these actions is as
follows. $\assumptiveS{i}$ can be executed if no $\assumptiveS{j}$,
$j \neq i$, has been executed from the same probabilistic term, and,
either $(\pp{probabilistic}~..p_i~(T_i)..)$ is in the root conjunct,
or it occurs in $T_k$ for some executed $\assumptiveS{k}$.
%%
Executing $\assumptiveS{i}$ in $s$ effects a transition to a successor
state $s^{T_i}$ with probability $p_i$, and $s^\bot$ with probability
$1 - p_i$. Here, $s^{T_i}$ is the union of $s$ with atomic terms from
$T_i$ and conflicting propositions from $s$ deleted. For example, if
the action adds $(=(\pp{is-in}~\pp{box})~\pp{office})$, then it must
delete $(=(\pp{is-in}~\pp{box})~\#)$. State $s^\bot$ is an added sink,
where $\forall\action\in\actions$ $\reward(\state^\bot, \action) = 0$
and $\transProb(\state^\bot, \action, \state^\bot) = 1$.

For sequential planning the operators from the POMDP model are
available with semantics that accommodate the above abstraction as
follows. In the deterministic model a proposition $\prop$ can be
thought to have a ternary interpretation at a state \state, as either
{\em true}, written $\prop\in\state$, {\em false}, written
$\prop\not\in\state$, or {\em unspecified}, with a slight abuse of
notation written $\prop\#\in\state$. For example, in $\pp{DORA}$
$(=(\pp{is-in}~\pp{box})\pp{office})\#\in\state_0$. For POMDP actions
$\action\in\actions$ in the deterministic model, if
$\prop \in \poss(\action)$, or if $\prop$ is the subject of a positive
or negative effect of $\action$, then $\action$ is not applicable
in \state\ if $\prop\#\in\state$. Indeed, first an assumptive action
must be applied to make a truth assignment to \prop, and then that
truth assignment could be modified by POMDP operators.

Addressing now the switching semantics of action execution. If
$\action\in\actions$ has a precondition that is not true with
probability $1$ in the underlying belief $\bstate$, then before it is
executed blindly, the system switches to a contingent session,
discussed in the following section. In detail, we halt the sequential
session at \action\ if $\exists
\state$ s.t. $\bstate(\state)>0$, 
$\prop\in\poss(\action)$ , and $\prop\not\in\state$. According to the
semantics of action execution there must be a $\state'$ s.t.
$\bstate(\state')>0$ and $\prop\in\state'$. Otherwise, \action\ must
not have been scheduled at \bstate.

then $\reward(\state,\action)=10$, and
otherwise if $\prop\not\in\state'$ then
$\reward(\state',\action)=-10$.

@@

\noindent which is equal to the maximal additive contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}, taking an FSC that corresponds to
the sequential plan.  In goal directed problems, where the only
non-zero reward is received at the first transition to a goal state,
the Eq~\ref{eq:tracevalue} criteria gives us the behaviour
of \system{FFR$_a$}~\cite{yoon:etal:2007}. From the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy. Finally, it is
worth clarifying that although the above discussion has been in terms
of a trace of length $N$, there is nothing in our approach that
artificially limits the length of candidate sequential plans.

@@

\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
-\$(T_i) & \pp{otherwise} \\
\end{array}
\]

\noindent Where $\$(T_i)$ is a positive numeric quantity which
captures the reward the agent receives for correctly rejecting a
false assumption. The added dual actions are propositionally trivial
-- i.e., $\forall\state\in\states$ $\poss(\assumptiveDT{i})
\subseteq \state$ and $\assumptiveDT{i}(\state) \equiv \state$.  
%%
In order to reduce the number of possible rejections we do not
consider assumptions that are not {\em active} with respect to the
action, $\action_i$, whose scheduled execution switch the system into
the contingent session. A assumption $\assumptiveS{i}$ is active if
$\action_i$ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix to $\action_i$. For
example, if $\pp{DORA}$'s trace is:

@@

\noindent Taking the switching action $\action_i$ to be
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$, we have that
$\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ is not
active, and therefore exclude
$\actions^{\bullet}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ from the
POMDP posed to the contingent session.

Again taking $\action_i$ to be the switching action, we include
another propositionally trivial action $\actions.\poss(\action_i)$
with the reward property:

\[
\reward(\state, \actions.\poss(\action_i)) = \bigg\{ \begin{array}{ll}
\$(\poss(\action_i)) & \pp{if}~\;\; \poss(\action_i) \subseteq \state \\
-\$(\poss(\action_i)) & \pp{otherwise} \\
\end{array}
\]

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\action_i)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\action_i)$ is executed,
then the current sequential plan is executed until further sensing is
scheduled, or to completion. In our project the rewards, i.e.,
function $\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture.

@@

\noindent At this point, the session would proceed in an
abstraction of the environment that does not contain a
$\pp{cup}$. With regards to abstraction, the contingent and serial
sessions apply the same applicability conditions ---i.e., that each
effect and condition $\prop$ is specified $\prop\in\state$
(resp. $\prop\#\in\state$)--- to actions from the DTPDDL problem
description.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states that occur with non-zero probability
according to that refined declaration remains of a practicable
size. In detail, for each excluded atomic term, we compute the {\em
entropy} of the corresponding proposition, {\em conditional} on the
active assumptions. The {\em conditional entropy} measure
is higher the more uncertain that proposition is given truth
assignments to propositions that are the subject of active
assumptions. Propositions that in the first place were excluded are
iteratively added to the problem posed to the conditional session in
increasing order according to that measure.

>>>>

We describe our approach that switches between sequential and
contingent sessions. As a continual planning approach, it proceeds by
interleaving planning and execution in a deterministic-action POMDP
described in DTPDDL. During a sequential session, planning is
performed by a ``classical'' system,\footnote{That is, a planner
designed to solve fully observable deterministic tasks.}  and
execution proceeds according to the {\em trace} computed by that
system. Taking the form of a classical plan, the trace specifies a
sequence of POMDP actions that achieve the agent's objectives in a
deterministic approximation, i.e., {\em determinisation}, of the
problem at hand. More precisely, the trace is an interleaved sequence
of POMDP actions and {\em assumptive} actions. The latter correspond
to assumptions the planner makes about the truth value of propositions
-- e.g. that a box of cornflakes is located in the kitchen at the
third plan step. They are called {\em applicability} assumptions if
the trace includes an action $\action$ that is not applicable with
probability $1$ at the belief-state
\bstate\ that the system is projected to be in when \action\ is
scheduled for execution, i.e., $\exists\state\in\states\;
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

Our approach always begins with a sequential session. Non-assumptive
actions from the trace are executed in sequence until the
applicability of the next scheduled action is uncertain. We denote
that action \switchAction.  A contingent session then begins, that
tailors sensory processing by the agent to determine whether the
assumptions made in the trace hold. 
%%
We add {\em disconfirm} and {\em confirm} actions to the model, so
that session is encouraged to judge the assumptions made in the
trace. On execution of one of those actions, control is returned to
the sequential session that continues at the {\em underlying}
belief-state.
%%
%% For each assumption we add a {\em
%% disconfirm} action to the POMDP whose execution is rewarding
%% (resp. costly) if the assumption is false (resp. true). We also add
%% one {\em confirm} action that is rewarding (resp. costly) to execute
%% if $\poss(\switchAction)$ is true (resp. false). If execution of the
%% contingent plan applies a disconfirm action, then a new sequential
%% session begins at the {\em underlying} belief-state. If the confirm
%% action is executed, the sequential session is resumed, and
%% \switchAction\ is executed. Otherwise, control rests in the continual
%% session.
%%
Because contingent planning is only practical in relatively small
POMDPs, contingent sessions plan in an abstract decision process
determined by the current trace. This abstraction is constructed by
first omitting all propositions that do not feature in the trace, and
by then iteratively refining the model while the result is of a
practicable size.

Finally, whether proceeding in a sequential or contingent session, our
continual planner maintains a factored representation of successive
belief-states, by performing belief revision according to
Eq~\ref{eq:revision}. Moreover, our internal representation of the
underlying belief-state corresponds more-or-less directly to an
$(\pp{:init})$ declaration. Our approach uses that distribution: (1)
as the source of candidate determinisations for sequential planning,
(2) to determine when to switch, and (3) as a mechanism to guide
construction of an abstract process for contingent sessions.

@@

A sequential session uses a classical planner to compute a trace. The
latter encapsulates assumptions about: (1) the true underlying state,
(2) how execution will progress, and (3) the possibility of the agent
eventually holding strong beliefs about the truth values of specific
state propositions. Here we describe the deterministic planning
problem, derived from the DTPDDL model, that admits plans which
correspond to traces.

In a deterministic-action POMDP all the uncertainty in state and
action is expressed in the $(\pp{:init})$ declaration. Our approach
uses the structure of that, as it occurs in the problem description,
to define a set of state-assumptions available to sequential planning.
%%
Writing \#\ if the value of a proposition is unspecified, for
$\pp{DORA}$ we have the following assumptions:

@@

\noindent An assumption corresponds to a {\em
relaxed} visitation of the root term of $(\pp{:init})$. In this
relaxed case, a conjunctive term is visited iff its atomic subterms
are visited, and zero or more of its immediate probabilistic subterms
are visited. The starting state, $\state_0$, for sequential planning
is an {\em abstract} state that captures the unique assumption which
has probability $1$. In $\pp{DORA}$, that is:

@@

In order to make assumptions available to the sequential planner, we
add one {\em assumptive} action $\assumptiveS{i}$ to the problem for
each element, $\prob_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. The physics of these actions is as
follows. $\assumptiveS{i}$ can be executed if no $\assumptiveS{j}$,
$j \neq i$, has been executed from the same probabilistic term, and,
either $(\pp{probabilistic}~..\prob_i~(T_i)..)$ is in the root
conjunct, or it occurs in $T_k$ for some executed
$\assumptiveS{k}$. Also, an assumption about a proposition
$\prop$ can only be made once, and must be sequenced before any POMDP
actions that have $\prop$ in their precondition or effect.
%%
In other words, an assumptive action
must be applied to make a truth assignment to \prop, and then that
truth assignment can be modified by the DTPDDL domain operators.
%%
%%
Executing $\assumptiveS{i}$ in $\state$ effects a transition to a
successor state $\state^{T_i}$ with probability $\prob_i$, and
$\state^\bot$ with probability $1 - \prob_i$. Here, $\state^{T_i}$ is
the union of $\state$ with atomic terms from $T_i$ with the
proposition denoting the undefined fact is deleted. For example, if
the action adds $(=(\pp{is-in}~\pp{box})~\pp{office})$, then it must
delete $(=(\pp{is-in}~\pp{box})~\#)$. State $\state^\bot$ is an added
sink, where $\forall\action$ $\reward(\state^\bot, \action) = 0$ and
$\transProb(\state^\bot, \action, \state^\bot) = 1$.
%%
Lastly, we have that if $\action$ has a precondition that is not true
with probability $\theta$, a given threshold, in the underlying belief
$\bstate$, then immediately before it is executed blindly the system
switches to a contingent session (described below).

%% For sequential planning the operators from the POMDP model are
%% available with semantics that accommodate the above abstraction as
%% follows: In the deterministic model a proposition $\prop$ can be
%% thought to have a ternary interpretation at a state \state, as either
%% {\em true}, written $\prop\in\state$, {\em false}, written
%% $\prop\not\in\state$, or {\em unspecified}, with a slight abuse of
%% notation written $\prop\#\in\state$. For example, in $\pp{DORA}$
%% $(=(\pp{is-in}~\pp{box})\pp{office})\#\in\state_0$. For POMDP actions
%% $\action\in\actions$ in the deterministic model, if
%% $\prop \in \poss(\action)$, or if $\prop$ is the subject of a positive
%% or negative effect of $\action$, then $\action$ is not applicable
%% in \state\ if $\prop\#\in\state$.

%% Addressing now the switching semantics of action execution. I
%% %% In detail, we halt the sequential
%% session at \action\ if $\exists
%% \state$ s.t. $\bstate(\state)>0$, 
%% $\prop\in\poss(\action)$ , and $\prop\not\in\state$. According to the
%% semantics of action execution there must be a $\state'$ s.t.
%% $\bstate(\state')>0$ and $\prop\in\state'$. Otherwise, \action\ must
%% not have been scheduled at \bstate.

%% then $\reward(\state,\action)=10$, and
%% otherwise if $\prop\not\in\state'$ then
%% $\reward(\state',\action)=-10$.

@@

\noindent which is equal to the maximal 
additive contribution a trace of the plan can make to
Eq~\ref{eq:expectedvalue}.  In goal directed problems, where the only
non-zero reward is received at the first transition to a goal state,
the Eq~\ref{eq:tracevalue} criteria gives us the behaviour sought
by \system{FFR$_a$}~\cite{yoon:etal:2007}. From the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy. Finally, it is
worth clarifying that although the above discussion has been in terms
of a trace of length $N$, there is nothing in our approach that
artificially limits the length of candidate sequential plans.

@@

\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
\hat\$(T_i) & \pp{otherwise} \\
\end{array}
\]

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a positive
(negative) numeric quantity which captures the utility the agent
receives for correctly (incorrectly) rejecting a false assumption. The
added dual actions are propositionally trivial -- i.e.,
$\forall\state\in\states$ $\poss(\assumptiveDT{i})
\subseteq \state$ and $\assumptiveDT{i}(\state) \equiv \state$.  
%%
In order to reduce the number of possible rejections we omit
assumptions that are not {\em active} with respect to the action,
\switchAction, whose scheduled execution switched the system into
the contingent session. An assumption $\assumptiveS{i}$ is active if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. For example, if $\pp{DORA}$'s trace is:

@@

\noindent Taking the switching action \switchAction\ to be
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$, we have that
$\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ is not
active, and therefore exclude
$\actions^{\bullet}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}))$ from the
POMDP posed to the contingent session.

We also include another propositionally trivial action
$\actions.\poss(\switchAction)$ with the reward property:

\[
\reward(\state, \actions.\poss(\switchAction)) = \bigg\{ \begin{array}{ll}
\$(\poss(\switchAction)) & \pp{if}~\;\; \poss(\switchAction) \subseteq \state \\
\hat\$(\poss(\switchAction)) & \pp{otherwise} \\
\end{array}
\]

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper we take $\hat\$(x)= - \$(x)(1 -
p) / p$, where $\$(x)$ is a given constant.

%%  We make no assumptions here about how they are
%% derived.

@@

\noindent At this point, the session would proceed in an
abstraction of the environment that does not contain a
$\pp{cup}$. With regards to abstraction, the contingent and serial
sessions apply the same applicability conditions ---i.e., that each
effect and condition $\prop$ is specified, $\prop\in\state$--- to
actions from the DTPDDL problem description.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero
probability according to that refined declaration remains of a
practicable size. In detail, for each excluded atomic term, we compute
the {\em entropy} of the active assumptions, {\em conditional} on the
corresponding proposition. Loosely speaking, the {\em conditional
entropy} measure is higher the more uncertain those assumptions are
given truth assignment to the proposition. Propositions that in the
first place were excluded are iteratively added to the problem posed
to the conditional session in increasing order according to that
measure.

%% In detail, for each excluded atomic term, we compute the {\em
%% entropy} of the corresponding proposition, {\em conditional} on the
%% active assumptions. The {\em conditional entropy} measure
%% is higher the more uncertain that proposition is given truth
%% assignments to propositions that are the subject of active
%% assumptions. Propositions that in the first place were excluded are
%% iteratively added to the problem posed to the conditional session in
%% increasing order according to that measure.
